---
title: "Untitled"
author: "RN7"
date: "9/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Packages 

```{r message=FALSE}
pacman::p_load(
  dplyr, tidyr, purrr, readr,
  stringr, tibble,
  glue, extrafont,
  ggplot2, magick,
  cowplot, patchwork,
  ggforce,
  rvest, polite,
  googledrive
)

extrafont::loadfonts()
```


* Team Totals
* Team by Game
* Player Totals
* Player by Game



# Data


```{r}

options(googledrive_quiet = TRUE)
googledrive::drive_auth(path = "~/.R/gargle/indigo-bazaar-325705-4c1134b651dc.json")

data_folder <- drive_ls(path = "Centre Circle Data & Info")

data_csv <- data_folder %>% filter(str_detect(name, ".csv")) %>% arrange(name)

# drive_find()
# drive_ls()
# 
# cpl2019_pbg <- drive_get(id = "1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg")
# cpl2019_pbg <- drive_read_raw(file = as_id("1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg"), type = "csv")

data_path <- here::here("data/CanPL_data")

#drive_download(file = data_csv[1,], path = paste(data_path, ))

data_name <- data_csv[1,][1]

#drive_download(file = as_id("1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg"), path = paste0(data_path, "/", data_name))





data_csv$name
data_csv$id

# g_id <- "1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg"
# data_name <- "CPLPlayerByGame2019.csv"


get_Drive_CPL_data <- function(g_id, data_name) {
  cat("... Trying to download", data_name, "...")
  
  safe_drive_download <- purrr::safely(drive_download)
  dl_return <- safe_drive_download(file = as_id(g_id), path = paste0(data_path, "/", data_name), overwrite = TRUE)
  
  if (is.null(dl_return$result)) {
    cat("\nSomething went wrong!\n")
  } else {
    res <- dl_return$result
    cat("\nFile:", res$name, "download successful!", "\nPath:", res$local_path, "\n")
  }
}

## Download all files from Google Drive!
map2(data_csv$id, data_csv$name,
     ~ get_Drive_CPL_data(g_id = .x, data_name = .y))

beepr::beep(8)

```


do via data_csv? Then can just add final path to local when successful. Even if fail, original should remain...?


- carve them up and upload them into thematic individual tables in a DB?
- create reports via RMD
- create Shiny app
- create Twitter bot


# Github Actions








```{r}
data_csv

data_path
```














# Misc


```{r}
CPL_playerTotal_2020 <- readr::read_csv(file = here::here("data/CPLPlayerTotals2020.csv"))
CPL_teamTotal_2020 <- readr::read_csv(file = here::here("data/CPLTeamTotals2020.csv"))
CPL_playerPG_2020 <- readr::read_csv(file = here::here("data/CPLPlayerByGame2020.csv"))
CPL_teamPG_2020 <- readr::read_csv(file = here::here("data/CPLTeamByGame2020.csv"))


CPL_playerTotal_2021 <- readr::read_csv(file = here::here("data/CPLPlayerTotals2021.csv"))
CPL_teamTotal_2021 <- readr::read_csv(file = here::here("data/CPLTeamTotals2021.csv"))
CPL_playerPG_2021 <- readr::read_csv(file = here::here("data/CPLPlayerByGame2021.csv"))
CPL_teamPG_2021 <- readr::read_csv(file = here::here("data/CPLTeamByGame2021.csv"))
```

```{r}
glimpse(CPL_teamTotal_2020)
```






```{r}
CPL_teamTotal_2021 %>% 
  select(ShotsTotal, xGPerShot, GM, Team, NonPenxG, PenTaken) %>% 
  mutate(NonPenShotsTotal = ShotsTotal - PenTaken,
         NonPenXGPerShot = NonPenxG / NonPenShotsTotal,
         NonPenShotsP90 = NonPenShotsTotal / (GM * 90) * 90,
         NonPenxGP90 = NonPenxG / (GM * 90) * 90)
```




- need to do work to flip everything and re-combine to get "against_" stats....





# League table

```{r}
library(gt)
```


```{r}
cpl_team_total_2021 <- read.csv(file = "data/CPLTeamTotals2021.csv")

glimpse(cpl_team_total_2021)
```

```{r}
cpl_team_pergame_2021 <- read.csv(file = here::here("data/CPLTeamByGame2021.csv"))

glimpse(cpl_team_pergame_2021)
```



```{r}
row1 <- cpl_team_pergame_2021 %>% slice_head(n = 2)

row1 %>% select(teamFullName, teamAbbrevName, opponentFullName, Win, Draw, Loss, Home, Away, Week, Result, GM, Date, Week) 
```

GM and Week are useless... number games by order of `Date`

```{r}
rowED <- cpl_team_pergame_2021 %>% filter(teamFullName == "Edmonton")

rowED %>% select(teamFullName, teamAbbrevName, opponentFullName, Win, Draw, Loss, Home, Away, Result, Date) 
```


