---
title: "Untitled"
author: "RN7"
date: "9/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Packages 

```{r message=FALSE}
pacman::p_load(
  dplyr, tidyr, purrr, readr,
  stringr, tibble,
  glue, extrafont,
  ggplot2, magick,
  cowplot, patchwork,
  ggforce,
  rvest, polite,
  googledrive
)

options(googledrive_quiet = TRUE)

extrafont::loadfonts()
```


* Team Totals
* Team by Game
* Player Totals
* Player by Game


# Instructions


## Google Drive 

Go to "Google Cloud Platform". Make sure you're already signed into your google account.

Go to "IAM & Admin" section on the left-side menu bar.

Create a new project. Give it a good name that states the purpose of your project.

Create service account. Fill in service account details. 

Select Role "Owner" or other as is relevant for your project.

Once done click on your service account from the project page.

Go to "Keys" tab and click on "ADD KEY" and then "Create new key".

Make sure the key type is "JSON" and create it.

Store the file in a secure space (make sure it's NOT being uploaded into a public repository on Github by .gitignore-ing the file or making it an environment variable)

Go to your Google Drive API page and enable the API. URL link is: https://console.developers.google.com/apis/api/drive.googleapis.com/overview?project={YOUR-PROJECT-ID}.

Have owner of folder/file share it with the service account. NOTE: Since the service account doesn't have a physical email inbox, you can't send an email with the link to it and open it from the email message. You have to make sure to share the folder/file from Google Drive directly.

## Github Actions

[Github Actions with R book](https://orchid00.github.io/actions_sandbox/)

- Have a github repository setup with the scripts and other materials you want to use.
- Open the repo up in RStudio and type in: `usethis::use_github_actions()`. This will do all the set up for you to get GHA running on your repository.
- Your GHA workflows are stored in `.github/workflows` as YAML files. If you used the function above it'll create one for R-CMD-check for you. You don't need to for what we're doing since this repository isn't a package. Either delete it or modify it for what we want to do.
- 


# Data


```{r}
googledrive::drive_auth(path = "~/.R/gargle/indigo-bazaar-325705-4c1134b651dc.json")

data_folder <- drive_ls(path = "Centre Circle Data & Info")

data_csv <- data_folder %>% filter(str_detect(name, ".csv")) %>% arrange(name)

# drive_find()
# drive_ls()
# 
# cpl2019_pbg <- drive_get(id = "1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg")
# cpl2019_pbg <- drive_read_raw(file = as_id("1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg"), type = "csv")

data_path <- here::here("data/CanPL_data")

#drive_download(file = data_csv[1,], path = paste(data_path, ))

data_name <- data_csv[1,][1]

#drive_download(file = as_id("1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg"), path = paste0(data_path, "/", data_name))





data_csv$name
data_csv$id

# g_id <- "1CS3aJ3LDjgw8Zi2myj3oE2Bvuikvuyeg"
# data_name <- "CPLPlayerByGame2019.csv"


get_Drive_CPL_data <- function(g_id, data_name) {
  cat("... Trying to download", data_name, "...")
  
  safe_drive_download <- purrr::safely(drive_download)
  dl_return <- safe_drive_download(file = as_id(g_id), path = paste0(data_path, "/", data_name), overwrite = TRUE)
  
  if (is.null(dl_return$result)) {
    cat("\nSomething went wrong!\n")
  } else {
    res <- dl_return$result
    cat("\nFile:", res$name, "download successful!", "\nPath:", res$local_path, "\n")
  }
}

## Download all files from Google Drive!
map2(data_csv$id, data_csv$name,
     ~ get_Drive_CPL_data(g_id = .x, data_name = .y))

beepr::beep(8)

```


do via data_csv? Then can just add final path to local when successful. Even if fail, original should remain...?


- carve them up and upload them into thematic individual tables in a DB?
- create reports via RMD
- create Shiny app
- create Twitter bot


# Github Actions








```{r}
data_csv

data_path
```














# Misc


```{r}
CPL_playerTotal_2020 <- readr::read_csv(file = here::here("data/CPLPlayerTotals2020.csv"))
CPL_teamTotal_2020 <- readr::read_csv(file = here::here("data/CPLTeamTotals2020.csv"))
CPL_playerPG_2020 <- readr::read_csv(file = here::here("data/CPLPlayerByGame2020.csv"))
CPL_teamPG_2020 <- readr::read_csv(file = here::here("data/CPLTeamByGame2020.csv"))


CPL_playerTotal_2021 <- readr::read_csv(file = here::here("data/CPLPlayerTotals2021.csv"))
CPL_teamTotal_2021 <- readr::read_csv(file = here::here("data/CPLTeamTotals2021.csv"))
CPL_playerPG_2021 <- readr::read_csv(file = here::here("data/CPLPlayerByGame2021.csv"))
CPL_teamPG_2021 <- readr::read_csv(file = here::here("data/CPLTeamByGame2021.csv"))
```

```{r}
glimpse(CPL_teamTotal_2020)
```






```{r}
CPL_teamTotal_2020 %>% 
  select(ShotsTotal, xGPerShot, GM, Team, NonPenxG, PenTaken) %>% 
  mutate(NonPenShotsTotal = ShotsTotal - PenTaken,
         NonPenXGPerShot = NonPenxG / NonPenShotsTotal)
```




- need to do work to flip everything and re-combine to get "against_" stats....

